On the Synchronization Power of the Openflow Data Plane

### 2015-04-21 inband-sync.tex
small fix

>>>>

As we will see, in the Openflow implementation of our mechanism, 
in addition to the ``normal'' configuration stored at the switch
(e.g., forwarding rules according to network policies), 
controllers will maintain additional information 
in the switch configuration: this information is used by the
controllers to synchronize.
